The Globular Cluster System of the Auriga Simulations

### 2019-03-06 AurigaGCS.tex
Updated the updated figures in the draft

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_M31_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \caption{
        Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \label{fig:MW-FeHRgc}
    }
\end{figure}

@@

Somewhat arbitrarily, I will take the region $r_p > 3$ kpc (containing 75 clusters) as the fiducial Mikly Way sample. If we were to view the Mikly Way at the same inclination angle to the disk as we see M31, this cutoff in projected distance would correspond roughly to the inner distance limits in the M31 halo sample.

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMR2dgc_withRatios-trim}.png}
    \caption{
        Mass-weighted distribution of (two-dimensional) galactocentric radii at 
        which star particles in the Auriga simulations are found. For Andromeda 
        we show the projected galactocentric radius, assuming its center is located
        at $(0^{\text{h}}42^{\text{m}}44.3^{\text{s}}, +41^{\circ}16'9")$ at a 
        distance of 778 kpc.
        \label{fig:Rgc}
    }
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted r$_{\text{gc}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total 
        mass in CR16 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{logMRgc_withRatios-trim}.png}
    \caption{
        Mass-weighted radial distribution of star particles in the Auriga 
        simulations. We show the median value of all Auriga haloes for all
        stars (orange dotted) and globular cluster candidates (i.e. stars with 
        age $>$~10~Gyr; orange solid). The latter sub set is further split up
        between stars that formed in-situ (blue solid), and those that were accreted
        (red solid). Shaded regions indicate the $1\sigma$ interval. The MW (M31)
        GCS is shown in purple (magenta). The middle (bottom) panel shows the
        ratio of the simulated mass to the mass in the MW (M31) GCS.
        \label{fig:Rgc}
    }
\end{figure}

\todo[inline]{
    Harris: `Somewhat arbitrarily, I will take the region $r_p > 3$ kpc 
    (containing 75 clusters) as the fiducial Milky Way sample. If we were to
    view the Milky Way at the same inclination angle to the disk as we see 
    M31, this cutoff in projected distance would correspond roughly to the 
    inner distance limits in the M31 halo sample.'
}

@@
